% LaTeX resume using res.sty
\documentstyle[fancyhead]{res} 

% Use \documentstyle[fancyhead,newcent]{res} to get New Century Schoolbook
% Postscript font; the fancyhead option is used to get 2 line header
% Use \documentstyle[fancyhead]{res} to get default (Computer Modern) font
\setlength{\topmargin}{-0.6in}  % Start text higher on the page 
\setlength{\textheight}{9.3in}  % increase textheight to fit more on a page
\addtolength{\textwidth}{-0.1in}  % increase textheight to fit more on a page
\setlength{\headrulewidth}{0pt} % suppress line drawn by default with fancyhead
\setlength{\headsep}{0.2in}     % space between header and text
\setlength{\headheight}{12pt}   % make room for header

\newdimen\mylinewidth 
\setlength{\mylinewidth}{\resumewidth}
\addtolength{\mylinewidth}{-0.4in}
\usepackage[left=1.5cm, right=2cm]{geometry}

\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }
%\newcommand{\lineunder}{\vspace*{-8pt} \\ \hspace*{-18pt} \hrulefill \\}
\newcommand{\lineunder}{\vspace*{-8pt} \\ \hspace*{-18pt} \rule{\mylinewidth}{0.5pt} \\}
\newcommand{\justline}{\hspace*{-18pt} \hrulefill \\\vspace{4pt}}
\newcommand{\header}[1]{{\hspace*{-15pt}\vspace*{2pt} \large{\textsc{#1}}} \vspace*{-2pt} \lineunder}
\newcommand{\contact}[3]{
\vspace*{-8pt}
\begin{center}
{\LARGE \scshape {#1}}
\lineunder
#2\\
#3
\end{center}
\vspace*{-8pt}
}

\lhead{\hspace*{-\sectionwidth}} % force lhead all the way left
\rhead{Page \thepage}  % put page number at right
\cfoot{}  % the footer is empty
\pagestyle{fancy} % set pagestyle for the document

\begin{document} 
\thispagestyle{empty} % this page does not have a header
\name{ARUNESH MISHRA}
\address{
Reno, NV.\\
Email: aruneshm@gmail.com}

\begin{resume}
\vspace{0.1in}
%\moveleft.5\sectionwidth\centerline{as a research intern for summer 2004.}  

\header{Interests}
Peer-peer networking and distributed system protocols for Blockchain Infrastructure. Deep Learn- ing for mobile applications. Wireless and Wired Networking Systems, Systems Security, Design of Scalable and Robust Systems, Location Inferencing from Wireless Networks, Location Security and Privacy
\header{Work Experience}
{\bf Feb 2017 - date}
    \begin{itemize}
        \item [] {\it Advisor and Mentor}, Zhongguancun Innovation Center, Santa Clara. \\
            Advising 4 startups on ML/Deep Learning, network design, strategy and pitch.
        \item [] {\it Advisor}, Latitude Blockchain Startup. \\ 
            Designing the Latitude protocol, blockchain and core whitepaper to disrupt mapping, telematics and insurance.
        \item [] {\it Research/Exploratory projects.} \\
            Wifi Expert app uses AI to solve problems on Android(30K daily active users, 4.4 rating).
            Safely (getsafely.net), AI based Assistant for physical safety. {\em Picolo} (https://picolo.network) a decentralized scalable database for blockchain apps.
    \end{itemize}

{\bf Jan 2008 - Feb 2017}
    \begin{itemize}
         \item[] {\it Tech Lead, Research Engineer roles}, Google, Mountain View, CA.\\
             Worked on 4 different projects, built backends and Android location infrastructure that serves more than 3
             Billion users every day. Participated in Google I/O demos. 30+ patents filed or issued.
    \end{itemize}

\header{Education}
{\bf Ph.D., Computer Science},
    \begin{itemize}
         \item[] Advisor: Dr. William Arbaugh, \\
		 Thesis: {\em Supporting Secure and Transparent Mobility in Wireless LANs} \\
                 University of Maryland, December 2005.
    \end{itemize}
{\bf B.Tech., Computer Science (President Gold Medalist)},
    \begin{itemize}
        \item[] Indian Institute of Technology, August 2000.
    \end{itemize}

\header{Other Contributions}
    \begin{itemize}
        \item [] {\bf Patents:} 30 patents issued, 21 pending.
        \item [] {\bf Open1x.org effort}: Engineered the first and widely used opensource implementation of the IEEE
            802.1X  for wifi security. Ships with linux distributions.
        \item [] {\bf Best paper award, Mobicom, 2009}: Awarded for the paper titled, ``Centaur: Realizing the Full Potential of Centralized WLANs through a Hybrid Data Path.".
        \item [] {\bf Google's Executive Management Group's Innovation Award, 2008}: Prestigious award presented by the
            C-Suite for innovative engineering work.
        \item [] {\bf President of India Gold Medal - 2000}: Awarded for highest GPA among all 2000-batch undergraduate students at IIT Guwahati.

        \item [] {\bf Student Rank One Merit Scholarship 1997-2000 IIT Guwahati}. Given to 1 student every semester. Won
            the award for 6 semesters consistently.

        \item [] {\bf Best Intern Award - 1999}: Awarded for best project intern at IBM India Research Labs, New Delhi. 

        \item [] {\bf Business Plan Award:} Business Competition - Runners up, 2002, University of Maryland Business School.

       \item [] Routinely invited to review papers in top tier conferences and journals.
    \end{itemize}
{\bf Media citations:}
    \begin{itemize}
         \item[$\bullet$] {\em Wired article on Nearby audio API},
             https://www.wired.com/story/ultrasonic-signals-wild-west-of-wireless-tech/.
         \item[$\bullet$] {\em Google Deducing Wireless Data}, on Slashdot and other Tech websites, Jan 29, 2010.
         \item[$\bullet$] {\em CNN, PCWorld, ZDNet News, Slashdot},  ``Researchers claim to crack
           wireless security'', Feburary 18, 2002.
         \item[$\bullet$] {\em CNET Asia}, ``Wireless network security shows cracks'', Feburary 19, 2002.  
         \item[$\bullet$] {\em BusinessWeek Online}, ``This LAN is Whose LAN?'', Feburary 21, 2002. 
    \end{itemize}
\end{resume}
\end{document}






























