% LaTeX resume using res.sty
\documentstyle[fancyhead]{res} 

% Use \documentstyle[fancyhead,newcent]{res} to get New Century Schoolbook
% Postscript font; the fancyhead option is used to get 2 line header
% Use \documentstyle[fancyhead]{res} to get default (Computer Modern) font
\setlength{\topmargin}{-0.6in}  % Start text higher on the page 
\setlength{\textheight}{9.3in}  % increase textheight to fit more on a page
\addtolength{\textwidth}{-0.1in}  % increase textheight to fit more on a page
\setlength{\headrulewidth}{0pt} % suppress line drawn by default with fancyhead
\setlength{\headsep}{0.2in}     % space between header and text
\setlength{\headheight}{12pt}   % make room for header

\newdimen\mylinewidth 
\setlength{\mylinewidth}{\resumewidth}
\addtolength{\mylinewidth}{-0.4in}

\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }
%\newcommand{\lineunder}{\vspace*{-8pt} \\ \hspace*{-18pt} \hrulefill \\}
\newcommand{\lineunder}{\vspace*{-8pt} \\ \hspace*{-18pt} \rule{\mylinewidth}{0.5pt} \\}
\newcommand{\justline}{\hspace*{-18pt} \hrulefill \\\vspace{4pt}}
\newcommand{\header}[1]{{\hspace*{-15pt}\vspace*{2pt} \large{\textsc{#1}}} \vspace*{-2pt} \lineunder}
\newcommand{\contact}[3]{
\vspace*{-8pt}
\begin{center}
{\LARGE \scshape {#1}}
\lineunder
#2\\
#3
\end{center}
\vspace*{-8pt}
}

\lhead{\hspace*{-\sectionwidth}} % force lhead all the way left
\rhead{Page \thepage}  % put page number at right
\cfoot{}  % the footer is empty
\pagestyle{fancy} % set pagestyle for the document
\begin{document} 
\contact{A r u n e s h \hspace{3mm}    M i s h r a}
{  San Francisco Bay Area.}
{aruneshm@gmail.com}
\thispagestyle{empty} % this page does not have a header

%\name{ARUNESH MISHRA}
%\address{\\6204 44th Ave,\\
%Riverdale, MD 20737.\\
%Email: arunesh@cs.umd.edu\\
%(408) 505 - 5086 (cell)\\
%(301) 405 - 8162 (off)}


\begin{resume}
%\moveleft.5\sectionwidth\centerline{as a research intern for summer 2004.}  
\header{Expertise}
Intelligent Automation, Knowledge-based answering systems and Deep Learning-based Chatbot systems (AI).
Peer-peer networking and distributed system protocols for privacy-centric decentralized applications, System and network
security.

\header{Work Experience}
    {\bf Founder/Engineer, Picolo Labs Inc}\hfill{\it May 2019 - date}
    \begin{itemize}
        \item [] {\it End-end encrypted Virtual Reality Applications}, Mountain View. \\
              Building the infrastructure technology for supporting high quality end-end encrypted
              applications in the VR space. NSF SBIR Phase I.
       \item [] {\it Multi-Lingual Offline Translator,} Mountain View. \\
              High-performance end-end speech recognition, language translation and speech-to-text models for 
              on-device inferencing. Key properties include support for 10+ languages with high accuracy through 
              technologies such as NN-pruning, Transformer-based learning and model quantizations.
    \end{itemize}
    {\bf Industry Expert Consultant}\hfill{\it  2017 - 2021 }
    \begin{itemize}
        \item [] {\it Advisor, Mentor and Research Scientist}, Z-Park Innovation Center, Santa Clara. \\
            Advising startups on Federated Learning technologies. Worked with 4 different startups on neural network design,
            implementation and data privacy/security considerations.
        \item [] {\it Advisor}, Blockchain Startups. \\ 
            Designing the Latitude protocol, blockchain and core
            whitepaper. Latitude is a blockchain that fundamentally shifts how data is shared in the Transportation
            Industry (Mapping, Telematics, Insurance).
        \item [] {\it Research projects.} \\
            Designed and implemented an app (30K daily active users, 4.4 rating) that fixes system problems on mobile
            phones using crowdsourced learning (deep learning). Worked on {\em Safely} -- an deep learning-based app for user safety vigilance
            and secure/safe contact tracing (Zero Interaction Authentication protocol).
    \end{itemize}

{\bf Jan 2013 - Feb 2017}
    \begin{itemize}
         \item[] {\it Tech Lead, Software Engineer}, Google, Mountain View, CA.\\

             Launched a network stack for peer-peer gaming on iOS and Android via Google Play Games SDK. Designed and
             implemented the network stack that maintains performance under changing network conditions and NAT
             topologies. Worked with the CEO of VectorUnit for RipTide demo at Google I/O to showcase the platform.
             Launched an API called Google Nearby that can transmit small amount of data securely over near-ultrasound
             for mobile phones. This can be used to authenticate people in same physical room and securely measure physical distance
             between phones to under 1 inch accuracy.
             Formed a team under Marissa Mayer to build an Android app that can automatically determine if two people
             are in the same physical room.
    \end{itemize}

{\bf Jan 2008 - Feb 2013}
    \begin{itemize}
         \item[] {\it Research Engineer}, Google, Mountain View, CA.\\

             Designed a purely crowdsourced-data based scalable system that computes user location using Wifi and Cellular base
             stations. System self-learns from Android users with a GPS fix to push location to indoor-users using
             statistical and randomized signal propagation algorithms.  System self-learns and scales to {\em 3 Billion
             queries} per day.
	 Conducted research in the area of software defined radios and
	 their application to urban environments for sensing mobile users and
	 traffic. Built cellular remap detection and localization technology, which
	 powers Google's Mobile Maps software (1B+ downloads, most popular
	 app on mobile).
	 
	 System is now used on Android, WinMo and Blackberry phones. Also works on browsers using HTML 5 Geolocation API, such
	 as on Mozilla's Firefox and Chrome browser, also launched with Google's Toolbar for Microsoft's Internet Explorer.
            Algorithms serves over 3 Billion location computations per day on Android and powers Google's mobile Ads
            business unit. The success of the Wifi project helped grow the team to 70 Engineers (from 3).

    \end{itemize}

{\bf Dec 2005 - Oct 2007},
    \begin{itemize}
         \item[] {\it Postdoc Research Scientist}, University of Wisconsin, Madison\\
	        $\bullet$ Designed an energy efficient VoIP over WiFi stack that
		enhances battery lifetime for wireless phones by a factor of 3.
		The new protocol stack uses innovative networking and systems
		concepts designed during the course of this research and have
		wider applicability. Filed three patents capturing the
		innovations in the field.\\
		$\bullet$ Worked on the problem of channel management (continued work from Maryland), published
		results at Sigmetrics and Mobicom. Initiated work on new ideas for WLAN architectures, collision detection and software-defined radios.\\
                $\bullet$ Managed a team of seven undergrad and graduate students working on a multitude of different research
projects  in the areas of WiFi, software-defined radios, city-wide mesh
networks and wireless emulation systems. Conducted world-class research and
published at top tier conferences and journals. Supervised research is being
pursued by current graduate students towards their PhD dissertations. Participated in activities
leading to the procurement of funding from government and private companies. Continue to collaborate and guide the
students till date. This research has won 3 best research awards at the ACM competitions over successive years.
%. Projects include channel management and power control in 802.11, research-level applications of the GNU radio, design 
%and implementation of inbuilding infrastructure and mesh testbeds, design of a monitoring system for a city-wide mesh
%network in Madison and realization of a scalable wireless network emulator system.
    \end{itemize}

\header{Education}
{\bf Ph.D., Computer Science},
    \begin{itemize}
         \item[] Advisor: Dr. William Arbaugh, \\
		 Thesis: {\em Supporting Secure and Transparent Mobility in Wireless LANs} \\
                 University of Maryland, December 2005.
    \end{itemize}

{\bf M.S., Computer Science},   	
    \begin{itemize}
         \item[] University of Maryland, August 2003.
    \end{itemize}

{\bf B.Tech., Computer Science (President Gold Medalist)},
    \begin{itemize}
          \item[] Indian Institute of Technology, August 2000.
    \end{itemize}


\header{Patents}\vspace{-0.7cm}

{\bf Issued:}
    \begin{itemize}
       \item [] [9,380,424] Crowdsourced signal propagation model.
       \item [] [9,377,523] Determining wireless access point locations using clustered data points.
       \item [] [9,355,387] System and method for event management and information sharing.
       \item [] [9,098,589] Geographic annotation of electronic resources.
       \item [] [8,989,101] Systems, methods, and computer-readable media for identifying virtual access points of
           wireless networks.
       \item [] [8,977,265] Method for performing handoff in wireless network.
       \item [] [8,954,094] Mobile device functions based on transportation mode transitions.
       \item [] [8,914,483] System and method for event management and information sharing.
       \item [] [8,868,762] Efficient proximity detection.
       \item [] [8,838,103] Method for performing handoff in wireless network.
       \item [] [8,837,360] Determining geographic location of network hosts.
       \item [] [8,830,909] Methods and systems to determine user relationships, events and spaces using wireless
           fingerprints.
       \item [] [8,825,078] Probabilistic estimation of location based on wireless signal strength.
       \item [] [8,719,426] Efficient proximity detection.
       \item [] [8,706,142] Probabilistic estimation of location based on wireless signal strength and platform
           profiles.
       \item [] [8,688,041] Methods and apparatus for secure, portable, wireless and multi-hop data networking.
       \item [] [8,498,592] Method and apparatus for improving energy efficiency of mobile devices through energy
           profiling based rate adaptation.
       \item [] [8,478,280] Minimum coverage area of wireless base station determination.
       \item [] [8,229,442] Derivation of minimum coverage of cellular sectors with cellular-site spatial density and
           application specific data.
       \item [] [8,218,493] System and method for interference mitigation in wireless networks.
       \item [] [8,150,367] System and method of determining a location based on location of detected signals.
       \item [] [8,085,719] System and method for achieving wireless communications with enhanced usage of spectrum
           through efficient use of overlapping channels.
       \item [] [8,064,921] Method and system for client-driven channel management in wireless communication networks.
       \item [] [8,005,114] Method and apparatus to vary the transmission bit rate within individual wireless packets
           through multi-rate packetization.
       \item [] [7,929,948] Method for fast roaming in a wireless network.
       \item [] [7,881,667] Methods and apparatus for secure, portable, wireless and multi-hop data networking.
       \item [] [7,421,268] Method for fast roaming in a wireless network.
       \item [] [7,400,604] Probing method for fast handoff in WLAN.
       \item [] [7,263,357] Method for fast roaming in a wireless network.
     \end{itemize}

\header{Recognition / Awards}
{\bf Best paper award, Mobicom, 2009}
    \begin{itemize}
         \item[] Awarded for the paper titled, ``Centaur: Realizing the Full Potential of Centralized WLANs through a Hybrid Data Path.".
    \end{itemize}

{\bf Google's Founder award for Innovation}
    \begin{itemize}
         \item[] Awarded by the Company's Founders for innovative work in
	 Location-based services for Mobile phones. Award was given to less than 30 Employees (out of 40K+).
    \end{itemize}

{\bf President of India Gold Medal - 2000}
    \begin{itemize}
         \item[] Awarded for highest GPA among all 2000-batch undergraduate students at IIT Guwahati.
    \end{itemize}

%\header{References}
%   \begin{itemize}
%	\item[] Available upon request.
%   \end{itemize}

%   \begin{itemize}
%	\item[] $\bullet$ Dr. Suman Banerjee, University of Wisconsin, (suman@cs.wisc.edu).
%        \item[] $\bullet$ Dr. William Arbaugh, University of Maryland, (waa@cs.umd.edu).
%	\item [] $\bullet$ Dr. Bobby Bhattacharjee, University of Maryland (bobby@cs.umd.edu).
%	\item [] $\bullet$ Dr. Jonathan Agre, Fujitsu Labs of America, (jagre@fla.fujitsu.com).
%   \end{itemize}
\end{resume}
\end{document}






























